Networked Character Devices

### 2011-12-11 report/paper.tex
Added Challenges section

>>>>

While Network Charter Devices provide a number of advantages, we have
also stumbled upon a number of challenges when it comes to properly
building and utilizing an NCD system. In particular, the NCD system:

\begin{packed_item}
\item Does not work well when Character Device file is not the exclusive
  device interface
\item Requires exported devices to be ``de-integrated'' from host system
\item Requires QOS guarantees and high quality network connection
\end{packed_item}

The original intention of the Unix and Linux \texttt{dev} file
system and the corresponding Charter Device file interface was to
provide the sole interface to device drivers. Today, while Character
Device file interfaces are still is use, they are no longer the sole
devise driver interface. Auxiliary systems like procfs
\cite{interfaces}, sysfs \cite{sysfs-mochel}, and netlink sockets
\cite{netlink-ayuso} provide supplementary and/or replacement interfaces
for the tradition Character Device file interface. Furthermore, some
dives interact directly with in-kernel subsystems (HID subsystem,
etc). Since our system
focuses on arbitrating the Charter Device file interface over the
network, use of these additional or alternate interfaces make devices
incompatible with the NCD system. This incompatibility can be mitigated
by extending the NCD system to include these alternate interfaces, but
breakdown of the original Unix ideal of having a dingle device driver
interface makes building system like NCD much more difficult and less
generalized.

Most modern Operating Systems, including Linux, assume that any device
physically connected to the system is available for the system to
use. As mentioned previously, Network Character Devices break down this
assumption. This one of the challenges involved in implementing an NCD
system is to remove the OS's assumption that any connected devices in
available for local use. Modern-day plug-and-play auto-configuration
system make this task even more difficult, and the means for breaking
down the availability assumption tends to be unique to a given
OS. Effectively removing this assumption is one of the larger,
still-open, NCD challenges.

Finally, since the NCD system makes a networked device appear as
though it is connect locally, the NCD system does not gracefully
handle situations that would never occur locally like network faults
and errors. Thus, the NCD system performs best when running on a
network with QOS guarantees and the necessary throughput to support all
NCD traffic.
